Supplemental Materials, Methods and Results

### 2021-04-29 supp.Rmd
Supplement update

   # Fit model
      PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + (1|ID), data=Predator)
      anova(PredatorAC)

@@

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
     ConspicDisplayCC2 <- lmer(dS ~ -1 + PopBRInt + (1|ID), data=Display_1)
     summary(ConspicDisplayCC2)

 # Contrasts hypothesis tests, but use RVE 
                 result2 <- Wald_test(ConspicDisplayCC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result2$p_val_bonfer <- sapply(p.adjust(result2$p_val, "bonferroni"), function(x) p_value(x))
# Posthoc tests
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(sqrt_dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))
## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

>>>>

   # Fit model
      PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + (1|ID), data=Predator)
      summary(PredatorAC)
      anova(PredatorAC)

@@

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
     PredatorAC2 <- lmer(dS ~ -1 + PopBRInt + (1|ID), data=Predator)
     summary(PredatorAC2)

 # Contrasts hypothesis tests, but use RVE 
                 result5 <- Wald_test(PredatorAC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result5$p_val_bonfer <- sapply(p.adjust(result5$p_val, "bonferroni"), function(x) p_value(x))
